\documentclass[11pt,letterpaper]{article}

% ATS Optimized Packages
\usepackage[margin=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% ATS-Friendly Settings (no colors, simple formatting)
\pagestyle{empty}
\raggedbottom
\raggedright

% Simple font setup (Times New Roman equivalent)
\usepackage{times}

% Reduce spacing for ATS parsing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Custom commands for formatting
\newcommand{\sectiontitle}[1]{
  {\large\textbf{#1}}
  \vspace{3pt}
}

\newcommand{\jobtitle}[4]{
  {\textbf{#1}} \hfill {#2} \\
  {\textit{#3}} \hfill {#4} \\
}

\newcommand{\bulletpoint}[1]{
  \textbullet \space #1
}

\begin{document}

% HEADER
\centerline{\textbf{\Large JOSE CARLOS HUERTA GARCIA}}
\vspace{2pt}
\centerline{
  +52 221 227 2775 $\cdot$ carlosj12336@gmail.com $\cdot$ github.com/jcarloshg $\cdot$ linkedin.com/in/jose-carlos-huerta-garcia-773952212/
}
\vspace{8pt}

% PROFESSIONAL SUMMARY
\sectiontitle{PROFESSIONAL SUMMARY}
Tech Lead and Full-Stack Software Architect with 5 years of experience specializing in designing and implementing scalable microservices using Domain-Driven Design, CQRS, and Clean Architecture. Proven expertise in cloud-native infrastructure on AWS, full-stack development across backend and frontend, and leading technical teams to deliver robust, high-availability systems. Experienced in mentoring engineers, establishing architectural standards, and translating complex technical decisions to business stakeholders.
\vspace{8pt}

% TECHNICAL SKILLS
\sectiontitle{TECHNICAL SKILLS}
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}

  \item \textbf{Programming Languages:} TypeScript, JavaScript, Python, Java, SQL, C++, C, C\#, Bash, Zsh

  \item \textbf{Backend Frameworks:} Spring Boot, NestJS, Express.js, FastAPI

  \item \textbf{Frontend Frameworks:} React, Angular, Next.js, React Native, Expo, Flutter

  \item \textbf{Architectural Patterns:} Domain-Driven Design (DDD), CQRS, Microservices, Clean Architecture, Hexagonal Architecture, Event-Driven Architecture

  \item \textbf{Databases:} PostgreSQL, MySQL, SQLite, MongoDB, DynamoDB, Prisma ORM, JPA, Spring Data

  \item \textbf{Cloud and DevOps:} AWS (CDK, CloudFormation, VPC, EC2, RDS, S3, Lambda, SQS, SNS, ELB, ASG, Route 53, Cognito, CodePipeline), Docker, Kubernetes, GitHub Actions, Tekton

  \item \textbf{Messaging and Integration:} Apache Kafka, WebSocket, REST APIs, TCP Microservices, Event Patterns

  \item \textbf{Testing and Quality:} Unit Testing, Integration Testing, End-to-End Testing, Jest, JUnit, Pytest

  \item \textbf{Data Science:} Machine Learning, Regression, Decision Trees, Random Forests, K-Means, PCA, Autoencoders, Pandas, NumPy, Matplotlib, Scikit-learn

  \item \textbf{Other Tools:} Git, GitHub, Bitbucket, Figma, NPM, Zod, MapStruct, Lombok
\end{itemize}
\vspace{8pt}

% PROFESSIONAL EXPERIENCE
\sectiontitle{PROFESSIONAL EXPERIENCE}

\jobtitle{Tech Lead, Full-Stack and Software Engineer with AWS}{September 2024 - October 2025}{DGMX Tech}{}
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{3pt}
  \item Strategic Architecture: Proposed and implemented Domain-Driven Design methodology, establishing new architectural standards for maintainability and scalability across the organization.
  \item Technical Leadership: Guided a Full Stack team using Scrum methodology, owning technical decisions regarding architecture, implementation strategy, and feature delivery to ensure client outcomes.
  \item Stakeholder Management: Managed communication and technical expectations with the client, aligning team efforts to support penetration of the Northern Mexico delivery app market.
  \item Talent Acquisition: Actively contributed to team growth by conducting technical interviews and assessments to maintain high engineering standards.
  \item Backend Development: Engineered and deployed robust, scalable, highly available solutions using AWS-CDK, establishing infrastructure with VPC, ELB, ASG, Route 53, SQS, SNS, IAM, EC2, RDS, S3.
  \item Frontend/Mobile Development: Developed and maintained intuitive customer interfaces on mobile using React Native (Expo), ensuring robust API integration with AWS backend.
\end{itemize}
\vspace{6pt}

\jobtitle{Front-End Developer}{March 2023 - July 2024}{Kokonut Company}{}
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{3pt}
  \item Core Development: Architected and maintained enterprise-level web applications with focus on Angular, React, and Next.js with complex API integrations.
  \item Agile Methodologies: Successfully delivered features using both Scrum and Waterfall methodologies, demonstrating adaptability to diverse project management approaches.
  \item Software Engineering Practices: Applied software engineering principles throughout the project lifecycle, including Use Case documentation for functional clarity.
  \item Stakeholder Communication: Delivered periodic sprint progress presentations, technical support, and continuous improvement proposals.
  \item Specialized Skills: Engineered immersive 3D environments within web applications using Three.js library with strict TypeScript for type safety.
\end{itemize}
\vspace{6pt}

\jobtitle{Software Engineer, Full-Stack with AWS, React Native, and UI/UX Design}{September 2021 - March 2023}{NIKU}{}
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{3pt}
  \item Backend Development: Engineered and deployed cloud-native solutions using AWS services with TypeScript APIs to deliver robust infrastructure.
  \item Mobile Application: Developed mobile delivery applications for food and logistics, translating product requirements into features.
  \item Design and User Experience: Designed and maintained UI/UX mockups for mobile applications, ensuring usability and user satisfaction.
  \item Technical Tools: Utilized JavaScript and TypeScript, managed NPM packages, Git version control, and built RESTful API integrations.
\end{itemize}
\vspace{8pt}

% EDUCATION
\sectiontitle{EDUCATION}

\jobtitle{Bachelor's Degree in Information Technology}{August 2017 - August 2022}{Benemérita Universidad Autónoma de Puebla}{}
\vspace{8pt}

% SOFT SKILLS
\sectiontitle{CORE COMPETENCIES}
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{3pt}
  \item Leadership and Mentorship: Demonstrated ability to guide technical teams and mentor engineers in software architecture and best practices.
  \item Strategic Communication and Translation: Proficient in explaining complex technical decisions to non-technical stakeholders and aligning technical strategy with business objectives.
  \item Systems Thinking: Ability to understand system interactions, anticipate downstream effects, and design holistic solutions for scalability and maintainability.
  \item Pragmatism and Critical Decision-Making: Strong at balancing technical perfection with business needs, making decisive architectural choices under constraints.
  \item Conflict Resolution and Stakeholder Management: Experienced in managing tensions between technical excellence and delivery timelines while maintaining team focus.
\end{itemize}
\vspace{8pt}

% KEY PROJECTS
\sectiontitle{NOTABLE PROJECTS AND ACHIEVEMENTS}

\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{3pt}
  \item \textbf{Microservices Architecture (CQRS Pattern):} Implemented CQRS pattern for inventory management system with stock reservations, real-time availability queries, and event-driven architecture using NestJS, PostgreSQL, and Jest testing.
  \item \textbf{Domain-Driven Design (DDD):} Designed and implemented DDD-based microservices with clear separation of domain, infrastructure, and application layers using TypeScript, NestJS, and Prisma ORM.
  \item \textbf{Cloud Infrastructure Automation:} Built AWS infrastructure as code using CDK, managing VPC, load balancing, auto-scaling, containerization, and CI/CD pipelines.
  \item \textbf{Event-Driven Messaging:} Architected event-driven systems using Apache Kafka for real-time messaging, distributed communication, and asynchronous processing across microservices.
  \item \textbf{Full-Stack Applications:} Delivered multiple full-stack applications across backend (NestJS, Spring Boot, FastAPI), frontend (React, Angular, Next.js), and mobile (React Native) platforms.
  \item \textbf{Data Science and Machine Learning:} Demonstrated expertise in machine learning techniques including regression analysis, decision trees, random forests, and cluster analysis using Python, Pandas, and Scikit-learn.
  \item \textbf{Clean Architecture and Testing:} Applied Clean Architecture principles with comprehensive testing strategies including unit, integration, and end-to-end tests using Jest and JUnit.
\end{itemize}

\end{document}
