\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Full Stack Developer with AI Expertise \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Full Stack Developer} with 5+ years of experience building SaaS, web applications, and mobile apps using \kw{JavaScript/TypeScript}, \kw{Next.js}, and \kw{NestJS}. Experienced applying \kw{AI to development workflows} for process optimization and automation. Proactive collaborator with strong English communication skills for meetings and technical discussions. Passionate about continuous learning and proposing innovative technical solutions.

\section*{EXPERIENCE}

\subsection*{DGMX Tech\hfill\textbf{Sep 2024 -- Present}}
\subsubsection*{Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Full Stack SaaS products}: Created scalable web applications using \tech{Next.js}, \tech{NestJS}, and \tech{TypeScript}, handling 10K+ daily requests with 99.9\% uptime.
    \item \textbf{Optimized with AI}: Implemented production-ready \kw{AI/LLM integrations} using \tech{AWS Bedrock} and \kw{OpenAI API} for automated customer support features, optimizing workflows and processes.
    \item \textbf{Used AI in development cycle}: Leveraged AI tools to accelerate development, code generation, and optimization throughout the software lifecycle.
    \item \textbf{Worked autonomously}: Executed projects independently while collaborating with the team, demonstrating proactivity in proposing technical solutions.
    \item \textbf{Built mobile and web apps}: Developed SaaS-type products using \tech{React Native} and \tech{Vue.js}, delivering real products launched and used by customers.
    \item \textbf{Drove continuous improvement}: Proposed architectural improvements using \kw{Domain-Driven Design (DDD)} and \kw{Clean Architecture}, improving maintainability by 60\%.
\end{itemize}

\subsection*{Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{Front-End Developer\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Built enterprise web applications}: Developed 4 SaaS-type web applications using \tech{Next.js}, \tech{React}, and \tech{TypeScript}, reducing production bugs by 40\%.
    \item \textbf{Applied AI in development}: Utilized AI-assisted development improve code quality and tools to accelerate delivery cycles.
    \item \textbf{Collaborated proactively}: Worked independently and as part of cross-functional teams, proposing technical solutions and improvements.
    \item \textbf{Executed agile methodology}: Delivered features using \kw{Scrum}, achieving 100\% sprint completion rate.
    \item \textbf{Implemented RESTful APIs}: Created efficient APIs integrating with frontend, optimizing data flow.
\end{itemize}

\subsection*{Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{Software Engineer (Full-Stack, AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed full-stack applications}: Built web and mobile applications using \tech{React Native}, \tech{Node.js}, and \tech{TypeScript}.
    \item \textbf{Built scalable SaaS products}: Architected cloud-native solutions on \tech{AWS}, supporting 50K+ daily users.
    \item \textbf{Proposed technical solutions}: Demonstrated proactivity in designing and implementing improvements.
    \item \textbf{Collaborated with teams}: Worked autonomously and collaboratively to deliver products on schedule.
    \item \textbf{Applied continuous learning}: Quickly adopted new technologies and frameworks as needed.
\end{itemize}

\section*{EDUCATION}

\subsection*{Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (Conversational B2 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \kw{CQRS}: Command Query Responsibility Segregation -- Codely, 2025 
    \kw{Agile Development and Scrum} -- IBM/Coursera, 2025, 
    \tech{Ultimate Docker} -- HolaMundo, 2025
\end{itemize}

\end{document}
