\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Software Engineer | Tech Lead \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Software Engineer} with 5+ and \kw{Tech Lead } with 1 years of experience designing, building, and scaling production-ready cloud-native applications. Specialized in \kw{algorithm development} and \kw{mathematical modeling} using \kw{Python}. Experienced in implementing computational solutions for complex problems with strong \kw{logical thinking} and \kw{problem-solving} abilities. Proven track record working autonomously in remote environments while collaborating with multidisciplinary teams. Expertise in \kw{Python (FastAPI)}, \kw{data analysis}, and \kw{computational modeling}.

\section*{EXPERIENCE}

\subsection*{\small DGMX Tech\hfill\textbf{Sep 2024 -- Oct 2025}}
\subsubsection*{\small Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Python Solutions}: Built and optimized computational pipelines using \tech{Python (FastAPI)}, implementing mathematical models for data processing and analysis, reducing processing time by 40\%.
    \item \textbf{Architected Cloud Solutions}: Guided migration of 3 legacy projects to scalable microservices using \kw{DDD} and Clean Architecture, improving maintainability by 60\%.
    \item \textbf{Designed High-Performance Systems}: Created algorithms for data processing workflows, handling 2K+ daily requests with 99.9\% uptime.
    \item \textbf{Provisioned AWS Infrastructure}: Architected and deployed cloud infrastructure using \tech{AWS CDK} (EC2, S3, Lambda, API Gateway, SQS, SNS, IAM, VPC).
    \item \textbf{Collaborated with Multidisciplinary Teams}: Worked with product, design, and business teams to translate requirements into technical solutions.
    \item \textbf{Drove Business Growth}: Oversaw stakeholder expectations and aligned technical roadmap, contributing to 25\% market penetration over 6 months.
    \item \textbf{Mentored Engineering Teams}: Directed 2 full-stack teams of 8 developers through \kw{Scrum} sprints, conducting 50+ code reviews and mentoring sessions.
\end{itemize}

\subsection*{\small Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{\small Front-End Developer\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Built Python Data Pipelines}: Developed data processing and analysis scripts using \tech{Python}, enabling real-time analytics for 4 enterprise applications.
    \item \textbf{Created Enterprise Web Applications}: Enhanced and maintained 4 enterprise applications using \tech{React}, \tech{Angular}, \tech{Next.js}, and \tech{Vue.js} with strict \tech{TypeScript}.
    \item \textbf{Implemented Mathematical Models}: Designed algorithms for data transformation and visualization, improving data processing accuracy by 35\%.
    \item \textbf{Championed Architectural Patterns}: Executed \kw{Hexagonal Architecture} and \kw{CQRS} patterns for scalable microservices.
    \item \textbf{Executed Agile Delivery}: Presented 4 critical features within deadlines using \kw{Scrum} methodology.
\end{itemize}

\subsection*{\small Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{\small Software Engineer (Full-Stack, AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Designed Scalable Systems}: Architected cloud-native solutions on \tech{AWS} (Lambda, API Gateway, RDS, DynamoDB), supporting 1K+ daily users.
    \item \textbf{Built Python Solutions}: Developed computational solutions using \tech{Python}, implementing algorithms for logistics optimization and data analysis.
    \item \textbf{Created RESTful APIs}: Enhanced robust APIs with \tech{Java (Spring Boot)}, \tech{Node.js (TypeScript)} and \tech{Python}, ensuring high performance.
    \item \textbf{Built Mobile Applications}: Constructed production-ready delivery apps (\tech{React Native}) for food and logistics.
    \item \textbf{Designed UI/UX}: Created high-fidelity mockups in \tech{Figma}, improving user experience metrics by 30\%.
\end{itemize}

\section*{EDUCATION}

\subsection*{\small Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (B1 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
AWS Certified Data Engineer Associate -- March 2026 (Ongoing)
\href{https://coursera.org/verify/HEG7YFDO6D1C}{Generative AI Applications with Amazon Bedrock} -- Coursera, March 2026
AWS Certified Data Engineer - Associate -- Udemy, March 2026 (Ongoing)
\href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications}{CQRS: Command Query Responsibility Segregation} -- Codely, October 2025
\href{https://academia.holamundo.io/certificates/fifvbfywmp}{Ultimate Docker} -- HolaMundo, July 2025
\href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications/1758852008410/single-media-viewer/?profileId=ACoAADXjsscBqtjtdk4S_qpdkHwZs, Fn9y9TiG0o}{Architectura Hexagonal} -- HolaMundo, April 2023
\end{document}