\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Frontend Developer | Tech Lead \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Frontend Developer} with 5+ and \kw{Tech Lead} 1 years of experience building responsive and accessible web applications using \kw{React}, \kw{Next.js}, \kw{JavaScript}, and \kw{TypeScript}. Skilled in consuming RESTful APIs using fetch, creating interactive user interfaces with success/error handling, and implementing SEO best practices. Proven ability to work independently and collaboratively in agile teams, with strong attention to detail and passion for creating visually appealing, user-friendly interfaces.

\section*{EXPERIENCE}

\subsection*{DGMX Tech\hfill\textbf{Sep 2024 -- Oct 2025}}
\subsubsection*{Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed frontend functionalities}: Built responsive user interfaces using \tech{React Native} and \tech{Vue.js}, improving mobile and web customer experience.
    \item \textbf{Implemented interactivity}: Created interactive components with success and error message handling, improving user satisfaction by 30\%.
    \item \textbf{Consumed APIs}: Integrated backend services using \tech{fetch API}, displaying results on dynamic web pages.
    \item \textbf{Wrote unit tests}: Implemented unit tests for own developments, ensuring code quality.
    \item \textbf{Managed version control}: Utilized \tech{Git} and \tech{GitHub} for version control, establishing code review processes.
    \item \textbf{Led frontend team}: Directed 2 full-stack teams through agile sprints, delivering critical products within deadlines.
\end{itemize}

\subsection*{Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{Front-End Developer\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed enterprise web applications}: Built and maintained 4 enterprise web applications using \tech{React}, \tech{Angular}, \tech{Next.js}, and \tech{Vue.js} with strict \tech{TypeScript}.
    \item \textbf{Created responsive interfaces}: Implemented responsive design with \tech{TailwindCSS}, ensuring cross-browser compatibility and accessibility.
    \item \textbf{Applied SEO best practices}: Optimized applications for search engines, improving organic visibility.
    \item \textbf{Consumed REST APIs}: Integrated multiple RESTful APIs using fetch and Axios, displaying results on dynamic interfaces.
    \item \textbf{Implemented interactivity}: Developed interactive components with state management, success and error messages.
    \item \textbf{Worked in agile methodology}: Executed sprints using \kw{Scrum}, achieving 100\% completion rate.
\end{itemize}

\subsection*{Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{Software Engineer (Full-Stack, AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed mobile applications}: Built delivery apps (food and logistics) using \tech{React Native}, achieving 4.5+ star user ratings.
    \item \textbf{Designed UI/UX interfaces}: Created high-fidelity mockups in \tech{Figma}, improving user experience metrics by 30\%.
    \item \textbf{Integrated APIs}: Consumed backend APIs using fetch, creating pages and displaying results.
    \item \textbf{Implemented responsive design}: Developed interfaces that adapt to different screen sizes.
    \item \textbf{Versioned code}: Utilized \tech{Git}/\tech{GitHub} for version control, reducing conflicts by 60\%.
\end{itemize}

\section*{EDUCATION}

\subsection*{Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (Conversational B2 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \kw{CQRS}: Command Query Responsibility Segregation -- Codely, 2025 
    \kw{Agile Development and Scrum} -- IBM/Coursera, 2025, 
    \tech{Ultimate Docker} -- HolaMundo, 2025
\end{itemize}

\end{document}
