\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Python Engineer | Tech Lead \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Python Engineer} with 5+ and \kw{Tech Lead } with 1 years of experience in software engineering with strong focus on \kw{Python} development, debugging, and problem-solving. Experienced building AI/LLM integrations and working with real codebases. Passionate about AI and LLM research, with strong analytical thinking and detail-oriented approach. Proficient in reconstructing technical reasoning and articulating complex solutions clearly.

\section*{EXPERIENCE}

\subsection*{DGMX Tech\hfill\textbf{Sep 2024 -- Present}}
\subsubsection*{Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Python Solutions}: Built scalable backend services using \tech{Python (FastAPI)}, handling 10K+ daily requests with 99.9\% uptime.
    \item \textbf{Applied AI/LLM Integration}: Implemented production-ready \kw{AI/LLM integrations} using \tech{AWS Bedrock} and \tech{OpenAI API} for automated features, demonstrating understanding of model reasoning and reasoning flows.
    \item \textbf{Debugging in Real Codebases}: Resolved complex bugs in microservices architecture, applying systematic debugging approaches and documenting decision points.
    \item \textbf{Used Git Workflows}: Managed code through \tech{Git}/\tech{GitHub} workflows including PRs, code reviews, and issue tracking.
    \item \textbf{Articulated Technical Reasoning}: Created comprehensive documentation and technical specs, demonstrating ability to explain complex technical decisions.
    \item \textbf{Contributed to Open Source}: Maintained internal libraries and tools, following open-source contribution best practices.
\end{itemize}

\subsection*{Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{Front-End Developer\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Built Python Backend Services}: Developed backend APIs using \tech{Python}, optimizing performance and reliability.
    \item \textbf{Debugged Complex Issues}: Resolved intricate bugs in enterprise applications, applying methodical debugging strategies.
    \item \textbf{Collaborated on Open-Source Tools}: Utilized and contributed to various open-source libraries and frameworks.
    \item \textbf{Applied Analytical Thinking}: Analyzed system requirements and designed efficient technical solutions.
\end{itemize}

\subsection*{Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{Software Engineer (Full-Stack, AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Python Applications}: Built backend services and APIs using \tech{Python}, ensuring technical accuracy.
    \item \textbf{Debugged Production Issues}: Resolved real-world bugs in production systems, documenting debugging logic and solutions.
    \item \textbf{Used Git Workflows}: Managed code with \tech{Git}/\tech{GitHub}, following best practices for branches, PRs, and merges.
    \item \textbf{Applied Problem-Solving}: Approached challenges methodically, reconstructing solution paths and articulating reasoning.
\end{itemize}

\section*{EDUCATION}

\subsection*{Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (Conversational B2 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications}{Introduction to Amazon Virtual Private Cloud (VPC)} -- Amazon Web Services (AWS), August 2025
    \item \href{https://academia.holamundo.io/certificates/fifvbfywmp}{Ultimate Docker} -- HolaMundo, July 2025
    \item Design and Analysis of Algorithms -- BUAP, July 2025
    \item Design Patterns in Java and PHP -- BUAP, July 2025
\end{itemize}

\end{document}
