\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Full Stack Developer | Tech Lead \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Full Stack Developer} with 5+ and \kw{Tech Lead} with 1 years of experience building SaaS, web applications, and mobile apps using \kw{JavaScript/TypeScript}, \kw{Next.js}, and \kw{NestJS}. Experienced applying \kw{AI to development workflows} for process optimization and automation, going beyond just copying code. Proactive collaborator with strong English communication skills for meetings and fluid communication. Passionate about continuous learning and proposing innovative technical solutions.

\section*{EXPERIENCE}

\subsection*{DGMX Tech\hfill\textbf{Sep 2024 -- Present}}
\subsubsection*{Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Full Stack SaaS Products}: Created scalable web applications using \tech{Next.js}, \tech{NestJS}, and \tech{TypeScript}, handling 10K+ daily requests with 99.9\% uptime.
    \item \textbf{Optimized with AI}: Implemented production-ready \kw{AI/LLM integrations} using \tech{AWS Bedrock} and \tech{OpenAI API} for automated customer support features, optimizing workflows and processes.
    \item \textbf{Used AI in Development Cycle}: Leveraged AI tools to accelerate development, code generation, and optimization throughout the software lifecycle.
    \item \textbf{Worked Autonomously}: Executed projects independently while collaborating with the team, demonstrating proactivity in proposing technical solutions.
    \item \textbf{Built Mobile and Web Apps}: Developed SaaS-type products using \tech{React Native} and \tech{Vue.js}, delivering real products launched and used by customers.
    \item \textbf{Drove Continuous Improvement}: Proposed architectural improvements using \kw{Domain-Driven Design (DDD)} and \kw{Clean Architecture}, improving maintainability by 60\%.
\end{itemize}

\subsection*{Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{Front-End Developer\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Built Enterprise Web Applications}: Developed 4 SaaS-type web applications using \tech{Next.js}, \tech{React}, and \tech{TypeScript}, reducing production bugs by 40\%.
    \item \textbf{Applied AI in Development}: Utilized AI-assisted development to improve code quality and accelerate delivery cycles.
    \item \textbf{Collaborated Proactively}: Worked independently and as part of cross-functional teams, proposing technical solutions and improvements.
    \item \textbf{Executed Agile Methodology}: Delivered features using \kw{Scrum}, achieving 100\% sprint completion rate.
    \item \textbf{Implemented RESTful APIs}: Created efficient APIs integrating with frontend, optimizing data flow.
\end{itemize}

\subsection*{Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{Software Engineer (Full-Stack, AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Full-Stack Applications}: Built web and mobile applications using \tech{React Native}, \tech{Node.js}, and \tech{TypeScript}.
    \item \textbf{Built Scalable SaaS Products}: Architected cloud-native solutions on \tech{AWS}, supporting 50K+ daily users.
    \item \textbf{Proposed Technical Solutions}: Demonstrated proactivity in designing and implementing improvements.
    \item \textbf{Collaborated with Teams}: Worked autonomously and collaboratively to deliver products on schedule.
    \item \textbf{Applied Continuous Learning}: Quickly adopted new technologies and frameworks as needed.
\end{itemize}

\section*{EDUCATION}

\subsection*{Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (Conversational B2 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications}{CQRS: Command Query Responsibility Segregation} -- Codely, October 2025
    \item \href{https://www.coursera.org/account/accomplishments/verify/D02Q5G7CT9H5}{Introduction to Agile Development and Scrum} -- IBM (Coursera), July 2025
    \item \href{https://academia.holamundo.io/certificates/fifvbfywmp}{Ultimate Docker} -- HolaMundo, July 2025
    \item \href{https://academia.holamundo.io/certificates/lsv1rybd6k}{Ultimate Linux} -- HolaMundo, July 2025
    \item \href{https://cursos.devtalles.com/certificates/80vdvpk0jq}{TanStack Query} -- DevTalles, July 2025
    \item \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications/1758852008410/single-media-viewer/?profileId=ACoAADXjsscBqtjtdk4S_qpdkHwZsFn9y9TiG0o}{Architectura Hexagonal} -- HolaMundo, April 2023
\end{itemize}

\end{document}
