\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Software Engineer (Front-End) | Tech Lead \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Software Engineer} with 5+ and \kw{Tech Lead} 1 years of experience building user interfaces and full-stack applications. Expert in \kw{React} and \kw{TypeScript} with proven track record delivering engaging, adaptive, and robust web solutions. Collaborated effectively with cross-functional teams including product, UX, and engineering to translate requirements into production features.

\section*{EXPERIENCE}

\subsection*{DGMX Tech\hfill\textbf{Sep 2024 -- Present}}
\subsubsection*{Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- México}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Web Features}: Built responsive web applications using \tech{React} and \tech{TypeScript}, delivering best-in-class user interfaces for 3+ projects.
    \item \textbf{Collaborated with Cross-Functional Teams}: Worked closely with product managers, UX designers, and engineers to translate requirements into engaging solutions, increasing user satisfaction by 40\%.
    \item \textbf{Conducted Code Reviews}: Performed 50+ code reviews to maintain high code quality, share knowledge, and uphold team development practices.
    \item \textbf{Troubleshot Technical Issues}: Resolved complex technical issues in production applications, reducing downtime by 60\%.
    \item \textbf{Applied Agile Methodologies}: Participated in \kw{Scrum} sprints, following agile development methodologies for iterative delivery.
    \item \textbf{Implemented Testing Practices}: Established unit, integration and end-to-end testing standards using \tech{Jest}, improving code coverage by 50\%.
\end{itemize}

\subsection*{Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{Front-End Developer\hfill Remote -- México}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Built User Interfaces}: Developed 4 enterprise web applications using \tech{React}, \tech{Next.js}, and \tech{TypeScript}, creating responsive and accessible user interfaces.
    \item \textbf{Collaborated with UX Teams}: Partnered with UX designers to implement user-centric designs, improving user engagement metrics by 35\%.
    \item \textbf{Applied Modern Patterns}: Implemented \kw{microfrontends (MFE)} architecture for scalable frontend applications.
    \item \textbf{Version Control with Git}: Managed code using \tech{Git}/\tech{GitHub}, including branches, merge conflicts, and collaborative workflows.
    \item \textbf{Optimized Performance}: Improved application load times by 45\% through code optimization and lazy loading.
    \item \textbf{Test-Driven Development}: Wrote comprehensive tests using \tech{Jest}, achieving 80\% code coverage.
\end{itemize}

\subsection*{Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{Software Engineer (Full-Stack, AWS)\hfill Remote -- México}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Front-End Features}: Built customer-facing applications using \tech{React} and \tech{TypeScript}, focusing on intuitive user experiences.
    \item \textbf{Designed RESTful APIs}: Created robust APIs integrating with frontend, applying knowledge of \kw{API design} and best practices.
    \item \textbf{Applied Data Structures and Algorithms}: Optimized application performance using efficient \kw{data structures} and \kw{algorithms}, reducing processing time by 40\%.
    \item \textbf{Version Control}: Maintained disciplined workflows with \tech{Git}/\tech{GitHub} for collaborative development.
    \item \textbf{Healthcare Application Development}: Built delivery app for food and logistics sector, demonstrating ability to develop healthcare-adjacent technology solutions.
\end{itemize}

\section*{EDUCATION}

\subsection*{Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (Conversational B2 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \kw{CQRS}: Command Query Responsibility Segregation -- Codely, 2025, \tech{AWS} VPC (Virtual Private Cloud) -- AWS, 2025, \kw{Agile Development and Scrum} -- IBM/Coursera, 2025, \tech{Docker} -- HolaMundo, 2025
\end{itemize}

\end{document}
