\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{keyword}{RGB}{43,43,43}
\definecolor{tech}{RGB}{43,43,43}
\color[RGB]{43,43,43}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{titlesec}

\newcommand{\kw}[1]{\textbf{\textcolor{keyword}{#1}}}
\newcommand{\tech}[1]{\textbf{\textcolor{tech}{#1}}}

\pagestyle{empty}
\geometry{a4paper, margin=0.5in}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\titleformat{\subsubsection}{\itshape}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsubsection}{0pt}{3pt}{3pt}
\titlespacing{\subsection}{0pt}{0pt}{0pt}

\begin{document}

\begin{center}
{\bfseries\LARGE Jose Carlos Huerta Garcia} \\
Fullstack (React, Python) | Tech Lead \\
(+52) 221 227 2775 | carlosj12336@gmail.com | \href{https://github.com/jcarloshg}{GitHub} | \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212}{LinkedIn}
\end{center}

\section*{PROFESSIONAL SUMMARY}
\kw{Fullstack (React, Python)} with 5+ and \kw{Tech Lead } with 1 years of experience designing, building, and scaling production-ready web applications with strong product and business focus. Specialized in \kw{UI/UX} techniques and \kw{AI-assisted development} using \kw{Claude Code} and \kw{LLMs}. Directing the development of reusable components with \kw{React}, \kw{Angular}, and \kw{JavaScript}. Oversaw communication with stakeholders to align technical solutions with business objectives. Delivered consistent, accessible, and high-performance user experiences.

\section*{EXPERIENCE}

\subsection*{\small DGMX Tech\hfill\textbf{Sep 2024 -- Oct 2025}}
\subsubsection*{\small Tech Lead, Full-Stack Engineer (AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Led Commercial CRM Redesign}: Directed the redesign of commercial CRM and communication flows with end customers, improving user engagement by 40\%.
    \item \textbf{Applied AI-Assisted Development}: Utilized \kw{Claude Code} and \kw{prompt engineering} to accelerate development cycles, reducing feature implementation time by 35\%.
    \item \textbf{Ensured Consistency and Accessibility}: Applied \kw{UI/UX} techniques ensuring WCAG compliance, achieving consistent and accessible experiences across all platforms.
    \item \textbf{Delivered High-Performance Interfaces}: Developed interactive interfaces with \tech{React}, \tech{Next.js}, and \tech{Vue.js}, optimizing performance to achieve sub-2-second load times.
    \item \textbf{Built Reusable Component Library}: Created scalable component library using \tech{React} and \tech{Angular} with \tech{TypeScript}, reducing development time by 50\% for new features.
    \item \textbf{Integrated Front-End with Back-End}: Integrated front-end services with robust APIs using \tech{Node.js (TypeScript)} and \tech{Python (FastAPI)}, handling 2K+ daily requests.
    \item \textbf{Contributed to Technical Architecture}: Took active role in roadmap discussions, prioritization, and rapid iterations, aligning technical decisions with business objectives.
    \item \textbf{Promoted Continuous Improvement}: Championed culture of continuous improvement and strong end-user focus, improving team velocity by 35\%.
    \item \textbf{Executed AI Integration}: Applied production-ready \kw{AI/LLM integrations} using \tech{AWS Bedrock}, enabling automated customer support features.
\end{itemize}

\subsection*{\small Kokonut Company\hfill\textbf{Mar 2023 -- Jul 2024}}
\subsubsection*{\small Front-End Developer\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Developed Enterprise Web Applications}: Enhanced and maintained 4 enterprise applications using \tech{React}, \tech{Angular}, \tech{Next.js}, and \tech{Vue.js} with strict \tech{TypeScript}, reducing production bugs by 40\%.
    \item \textbf{Applied UI/UX Techniques}: Applied rigorous \kw{UI/UX} methodologies, improving user experience metrics by 30\% and ensuring accessibility standards.
    \item \textbf{Built Scalable Components}: Developed scalable components with proper state management, supporting 50K+ daily active users.
    \item \textbf{Integrated APIs}: Integrated front-end services with back-end APIs, working with distributed architectures to ensure seamless data flow.
    \item \textbf{Executed Agile Delivery}: Presented 4 critical features within deadlines using \kw{Scrum} methodology, achieving 100\% sprint completion rate.
\end{itemize}

\subsection*{\small Niku\hfill\textbf{Sep 2021 -- Mar 2023}}
\subsubsection*{\small Software Engineer (Full-Stack, AWS)\hfill Remote -- Mexico}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Designed User Interfaces}: Created intuitive and high-performance user interfaces using \tech{React} and \tech{React Native}, achieving 4.5+ star user rating.
    \item \textbf{Integrated APIs}: Developed robust API integrations ensuring seamless communication between front-end and back-end systems.
    \item \textbf{Designed UI/UX}: Created high-fidelity mockups in \tech{Figma}, improving user experience metrics by 30\%.
    \item \textbf{Applied Business Orientation}: Translated product and business requirements into functional and efficient features, driving business growth.
\end{itemize}

\section*{EDUCATION}

\subsection*{\small Benemerita Universidad Autonoma de Puebla}
Bachelor's Degree in Information Technology \hfill Aug 2017 -- Aug 2022

\section*{LANGUAGES}
Spanish (Native), English (Conversational B2 -- TOEFL ITP 453 points, Mar 2025)

\section*{CERTIFICATIONS}
    \href{https://coursera.org/verify/HEG7YFDO6D1C}{Generative AI Applications with Amazon Bedrock} -- Coursera, March 2026
    \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications}{CQRS: Command Query Responsibility Segregation} -- Codely, October 2025
    \href{https://academia.holamundo.io/certificates/fifvbfywmp}{Ultimate Docker} -- HolaMundo, July 2025
    \href{https://www.linkedin.com/in/jose-carlos-huerta-garcia-773952212/details/certifications/1758852008410/single-media-viewer/?profileId=ACoAADXjsscBqtjtdk4S_qpdkHwZs, Fn9y9TiG0o}{Architectura Hexagonal} -- HolaMundo, April 2023
    \href{https://www.coursera.org/programs/knu-high-o3k80/learn/continuous-integration-and-continuous-delivery-ci-cd?source=search}{Continuous Integration and Continuous Delivery (CI/CD)} -- IBM, Ongoing

\end{document}
